### 2023-11-11 manuscript/manuscript.Rmd
Add retention time difference limit for LC-MS to adduct and isotopic assignment iteration section
replace unambiguous with singular

For each sample matrix, the input data for molecular formula assignment had undergone spectral processing and pre-treatment and consisted of a sample by *m/z* feature intensity matrix containing both positive and negative ionisation mode data. 
Molecular formula assignment was conducted using the R package *assignments* v`r packageVersion('assignments')` and the approach comprised four major steps which are outlined in Figure \@ref(fig:figure-1-approach).
Where assignment was possible, *m/z* features were designated with unambiguous molecular formulas, isotopes and ionisation adduct assignments. 
The following sections outline the methodology behind each major step of the approach.

@@

This first assignment step used only positively correlated feature relationships that corresponded to adduct and isotopic relationships without transformation. 
This assignment step consisted of molecular formula generation, molecular formula selection (Section \@ref(MF-selection)) and then multiple iterations of network graph component assembly and network graph component selection (Section \@ref(component-selection)).

>>>>

For each sample matrix, the input data for molecular formula assignment had undergone spectral processing and pre-treatment and consisted of a sample by *m/z* feature intensity matrix containing both positive and negative ionisation mode data. 
Molecular formula assignment was conducted using the R package *assignments* v`r packageVersion('assignments')` and the approach comprised four major steps which are outlined in Figure \@ref(fig:figure-1-approach).
Where assignment was possible, *m/z* features were designated with singular molecular formula, isotope and ionisation adduct assignments. 
The following sections outline the methodology behind each major step of the approach.

@@

This first assignment step used only positively correlated feature relationships that corresponded to adduct and isotopic relationships without transformation. 
For the C18-UHPLC-HRMS data, these correlated feature relationships were limited to *m/z* features with a retention time difference of up to 2 seconds.
This assignment step consisted of molecular formula generation, molecular formula selection (Section \@ref(MF-selection)) and then multiple iterations of network graph component assembly and network graph component selection (Section \@ref(component-selection)).
